Tungsten Disulfides and Tungsten Oxides Core-Shell NWs

### 2015-01-14 ch-tms/tmspart.tex
coreshell chapter revised

\section{Introduction}
\subsection{Properties of TMDCs}
Tungsten disulfide (\ce{WS2}) is a group VI dichalcogenide semiconductor compound. The molecular weight is 249.97 \si{g\per \mole}. Almost all natural \ce{WS2} belongs to P63/mmc space group (2H-\ce{WS2}), where $a$ is 3.153 \si{\angstrom}, $c$ is 12.323 \si{\angstrom} (PDF 04-003-4478). Two other crystal structures were found in man-made \ce{WS2}, i.e., 1T and 3R, where 3R can be prepared by bromine (Br) chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011}

As a reference, the lattice dimensions are summarized in Table~\ref{tab:ms2lattice}.
%lattice
\begin{table}[htb]
\centering
\caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
\begin{tabular}{lccr}
\toprule
         &  & 2H-\ce{MoS2}\cite{Coehoorn1987,Ataca2012} & 2H-\ce{WS2}\cite{Albe2002,Schutte1987} \\
\midrule
Lattice constant & a(\AA) & 3.1604 & 3.171 \\
                 & c(\AA) & 12.295 & 12.359 \\
Within \ce{MS2} layer & M-3S (\AA)& 2.37  & 2.405   \\
                      & S-1S (\AA)& 3.11  & 3.14   \\
Between \ce{MS2} layer& S-3S (\AA)&   & 3.53   \\
\bottomrule
\end{tabular}
\end{table}

The geometrical symmetry groups of WS2 NT.\cite{Milosevic2000} The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \si{\angstrom}. This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube. The diameter of a nanotube is given by 
\begin{equation}
d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}.
\end{equation}
Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the $\cos\pi/3 \times 2 = 1$. In analog with carbon nanotube, chiral angle $\theta$ is given by
\begin{equation}
\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}.
\end{equation}
Chiral angles from the interval $[0,\pi/6]$ is sufficient for all possible tubes. Tubes $(n,0)$ with zero chiral angle are named zigzag, tubes $(n,n)$ with $\pi/6$ chiral angle are armchair, whereas all others are referred as chiral ones with $\theta \in (0,\pi/6)$. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{ws2_tube1}
\caption[\ce{WS2} nanotube rolling]{\ce{WS2} nanotube rolling}
\label{fig:ch5ntroll}
\end{figure}

\subsection{Synthesis Review of TMDCs}
Shortly after the discovery of \gls{cnt} in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e., \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well. \citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Hence this study just recapitulates the main categories of synthesis methods:
\begin{enumerate}
\item Reducing \ce{MO3} in \ce{H2} and \ce{H2S} atmosphere;\footnote{M = Mo, W in this work}
\item Direct decomposition of \ce{MS3};
\item Decomposition of the ammonium salt \ce{(NH4)2MS4};
\item Using CNT as templates, arc discharge, or laser ablation.
\end{enumerate}
Except the aforementioned methods, another important reaction in CVD domain is
\begin{align}
\cee{WCl6 + S &\rightarrow WS2 + Cl2S2}\\
\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
\end{align}
This reaction has been explored by several authors\cite{Stoffels1999} and could be used under atmospheric pressure.\cite{Li2004a}

@@

\subsection{Raman on WS$_2$: Bulk, FL and NTs}\label{sec:ntram}

>>>>

\section{Introduction}
\subsection{Properties and Applications of WS$_2$}
Tungsten disulfide (\ce{WS2}) is a group VI dichalcogenide semiconductor compound. The molecular weight is 249.97 \si{g\per \mole}. Almost all natural \ce{WS2} belongs to P63/mmc space group (2H-\ce{WS2}), where $a$ is 3.153 \si{\angstrom}, $c$ is 12.323 \si{\angstrom} (PDF 04-003-4478). Two other crystal structures were found in man-made \ce{WS2}, i.e., 1T and 3R, where 3R can be prepared by bromine (Br) chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011} As a reference, the lattice dimensions are summarized in Table~\ref{tab:ms2lattice}.
%lattice
\begin{table}[htb]
\centering
\caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
\begin{tabular}{lccr}
\toprule
         &  & 2H-\ce{MoS2}\cite{Coehoorn1987,Ataca2012} & 2H-\ce{WS2}\cite{Albe2002,Schutte1987} \\
\midrule
Lattice constant & a(\AA) & 3.1604 & 3.171 \\
                 & c(\AA) & 12.295 & 12.359 \\
Within \ce{MS2} layer & M-3S (\AA)& 2.37  & 2.405   \\
                      & S-1S (\AA)& 3.11  & 3.14   \\
Between \ce{MS2} layer& S-3S (\AA)&   & 3.53   \\
\bottomrule
\end{tabular}
\end{table}

\ce{WS2} can also form tubular structures in analog with those of carbon nanotubes. The geometrical symmetry group of \ce{WS2} NT has been reported.\cite{Milosevic2000} The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \si{\angstrom}. This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube. The diameter of a nanotube is given by 
\begin{equation}
d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}.
\end{equation}
Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the $\cos\pi/3 \times 2 = 1$. In analog with carbon nanotube, chiral angle $\theta$ is given by
\begin{equation}
\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}.
\end{equation}
Chiral angles from the interval $[0,\pi/6]$ is sufficient for all possible tubes. Tubes $(n,0)$ with zero chiral angle are named zigzag, tubes $(n,n)$ with $\pi/6$ chiral angle are armchair, whereas all others are referred as chiral ones with $\theta \in (0,\pi/6)$. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_tube1}
\caption[\ce{WS2} nanotube rolling]{\ce{WS2} nanotube rolling}
\label{fig:ch5ntroll}
\end{figure}

\subsection{Synthesis Review on WS$_2$}
Shortly after the discovery of \gls{cnt} in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e., \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well. \citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Hence this study just recapitulates the main categories of synthesis methods:
\begin{enumerate}
\item Reducing \ce{MO3} in \ce{H2} and \ce{H2S} atmosphere;\footnote{M = Mo, W in this work}
\item Direct decomposition of \ce{MS3};
\item Decomposition of the ammonium salt \ce{(NH4)2MS4};
\item Using CNT as templates, arc discharge, or laser ablation.
\end{enumerate}
Except the aforementioned methods, another important reaction in CVD domain is
\begin{align}
\cee{WCl6 + S &\rightarrow WS2 + Cl2S2}\\
\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
\end{align}
This reaction has been explored by several authors\cite{Stoffels1999} and could be used under atmospheric pressure.\cite{Li2004a}

@@

\subsection{Raman on WS$_2$: Bulk, Few Layer and Nanotube}\label{sec:ntram}
